Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-19 RNARedPrint.tex

\paragraph{Central computational problem.}
Let us consider $k$ features $F_1,\dots F_k$ to target all of them simultaneously. We base our strategy for targeting the $k$ features $F_1,\dots,F_k$ on generating samples from a Boltzmann distribution parameterized by weights $\pi_1,\dots,\pi_k$, one for each feature. These weights essentially allow us to shift the sample distributions towards specific targets.
Sampling from this distribution requires to compute corresponding partition functions, such that we can draw sequences with probabilities proportional to their Boltzmann weight:
\begin{equation}
\label{eq:sample-distribution}
\Pr(S|\pi_1,\dots,\pi_k) \propto \prod_{1\leq \ell\leq k} \pi_\ell^{-F_\ell(S)}.
\end{equation}

@@

\section*{Conclusion}
%%!!!!!!!!!!!!!!! consider to merge into disciussion
%Going beyond our encoding of the base pair model energy features and the \GCb\% feature, the contributions provide more generality and allow expressing complex features of the
%sequences alone, e.g.\ rewarding or penalizing specific sequence
%motifs, as well as features depending on the target structures.
%Furthermore, constraints, which enforce or forbid features, are
%naturally expressed by assigning infinite penalties to invalid
%(partial) sequences (even if in implementations, explicit handling of constraints is advantageous). In particular, the %framework
%aptures various RNA energy models, they can be handled efficiently (in the sense of FPT), as long as the dependencies of their additive energy contributions are bounded.

>>>>

\paragraph{Central computational problem.}
Let us consider $k$ features $F_1,\dots F_k$ to target all of them simultaneously. We base our strategy for targeting the $k$ features $F_1,\dots,F_k$ on generating samples from a Boltzmann distribution parametrized by weights $\pi_1,\dots,\pi_k$, one for each feature. These weights essentially allow us to shift the sample distributions towards specific targets.
Sampling from this distribution requires to compute corresponding partition functions, such that we can draw sequences with probabilities proportional to their Boltzmann weight:
\begin{equation}
\label{eq:sample-distribution}
\Pr(S|\pi_1,\dots,\pi_k) \propto \prod_{1\leq \ell\leq k} \pi_\ell^{-F_\ell(S)}.
\end{equation}

@@

\section*{Conclusion}
%%!!!!!!!!!!!!!!! consider to merge into discussion
%Going beyond our encoding of the base pair model energy features and the \GCb\% feature, the contributions provide more generality and allow expressing complex features of the
%sequences alone, e.g.\ rewarding or penalizing specific sequence
%motifs, as well as features depending on the target structures.
%Furthermore, constraints, which enforce or forbid features, are
%naturally expressed by assigning infinite penalties to invalid
%(partial) sequences (even if in implementations, explicit handling of constraints is advantageous). In particular, the %framework
%captures various RNA energy models, they can be handled efficiently (in the sense of FPT), as long as the dependencies of their additive energy contributions are bounded.
